### 2017-05-03 paper2.tex
Add files via upload

Inter-site comparison is the crux of UHI analysis, thus it is imperative that urban T\textsubscript{surf} measurements are representative of coherent urban patches and free from confounding influences (i.e. atmospheric and emissivity effects). Meta-analysis of the air temperature (T\textsubscript{air}) UHI literature shows that these goals are rarely satisfied \citep{Stewart2011}. Given the relative difficulty in retrieving accurate, representative urban T\textsubscript{surf}, similar conclusions are likely for sUHI analysis. In spite of this fact, and the short period over which large-scale, generalizable methods for measuring urban T\textsubscript{surf} have been available, study of sUHI via TIR remote sensing has expanded significantly in the last twenty years \citep{Peng2012,Voogt2003}. Using the method described in Chapter \ref{paper1} an 8-month climatology of hemispherical radiometric urban T\textsubscript{surf} (T\textsubscript{hem, r}) was derived from time continuous near-ground upwelling TIR as measured from an inverted pyrgeometer. The method was developed to address and overcome biases inherent in traditional methods for urban T\textsubscript{surf} retrieval by providing temporally continuous, geometrically representative\footnote{A hemispherical view is not perfectly geometrically representative of urban surface geometry. This is best illustrated by visualizing an urban area from the perspective of a downward facing ‘fish-eye’ camera. Geometric sampling biases are a result of lens distortions and the sensor cosine response. However, by sampling the surface 3-dimensionally, T\textsubscript{hem, r} is more representative of urban geometry than conventional 2-dimensional views of the surface. The geometric representivity of urban T\textsubscript{hem, r} is discussed in section \ref{Methodological limitations and considerations}.} urban T\textsubscript{surf} under all-sky conditions for sUHI analysis. These measurements are often made as a part of the net radiation determination for urban energy balance studies.

@@

\subsection{A method to retrieve hemispherical radiometric urban T\textsubscript{surf}}

@@

For each time step, these steps are repeated at an interval of 0.5 \si{\kelvin} for a predefined range of potential T\textsubscript{hem, r}, with results aggregated into a lookup table relating modeled irradiances to corrected T\textsubscript{hem, r} for the observed ambient T\textsubscript{air} and humidities. The measured irradiance is then matched with the closest modeled irradiance to return the associated corrected T\textsubscript{hem, r} for the target time step. sUHI magnitudes for the study area are calculated as the difference between urban T\textsubscript{hem, r} and rural T\textsubscript{hem, b} with rural T\textsubscript{hem, b} calculated via

\begin{equation}
\label{ruralt}
T_{hem,~ b} = \sqrt[4]{\frac{\epsilon L_z^\uparrow + (1 - \epsilon)L_{sky}^\downarrow}{\sigma}}
\end{equation}.

\noindent where $L_z^\uparrow$ is at-sensor upwelling longwave radiation, $L_{sky}^\downarrow$ is at-sensor reflected downwelling longwave radiation, and emissivity ($\epsilon$) = 0.94.

Sensitivity tests included in Section \ref{sensitivity} of the companion paper show that screen level irradiances ($ z $ = ~2 \si{\meter}) are not subject to significant effects from the intervening atmosphere and do not require atmospheric correction. Rural irradiances in this study were measured from approximately 2 \si{\meter} above ground, thus rural T\textsubscript{hem, b} is approximately equal to T\textsubscript{hem, r}.

@@

To evaluate the method

@@

T\textsubscript{hem, r} are retrieved from radiation and meteorological data collected from December 2001 through July 2002 as a part of the Basel Urban Boundary Layer Experiment (BUBBLE) campaign conducted in Basel, Switzerland \citep{Rotach2005}. Urban data were observed from a tower located near city center at the "Basel Sperrstrasse" site. Rural reference data were observed at the "Lange Erlen" site approximately 6 \si{\kilo \meter} to the north east in the outskirts of the city of Basel. Urban and rural site morphologies and observed variables are described in Table \ref{morphbspr}.

\begin{table}[H]
	\centering
	\caption{A description of morphological and measured variables for urban and rural sites. Modified from \citet{Rotach2005} to include only relevant parameters.}
	\label{morphbspr}
	\begin{tabular*}{\textwidth}{p{3.75cm} p{2.25cm}p{3.5cm}p{2.75cm}p{2.75cm}}
		\toprule 
		Site & Location & Morphological & Meteorological & Radiation \\ 
		& Height & Characteristics\footnote{} & Variables\footnote{} & [No of levels]\footnote{} \\ 	\midrule

		Basel Sperrstrasse \newline \textit{Urban} \textit{street canyon} \newline LCZ: 2 & 47.57\si{\degree} N \newline 7.60\si{\degree} E \newline 255 \si{\meter} a.s.l. & $z_H$ = 14.6  \si{\meter} \newline $\sigma_H $ = 6.9 \si{\meter} \newline H/W = 0.54 \newline $\lambda_C $ = 0.37\newline $\lambda_S$ = 1.0 \newline $\alpha$ = 11.0\% & T\textsubscript{air} [7] \newline H [7] \newline WV [12] \newline WD [1] \newline P [1] & L\textsubscript{up} [3] \newline L\textsubscript{down} [5] \newline S\textsubscript{up} [2] \newline S\textsubscript{down} [3] \\ 
		& & & & \\
		Lange Erlen \newline \textit{Rural parkland} \newline LCZ: B & 47.59\si{\degree} N \newline 7.65\si{\degree} E \newline 240 \si{\meter} a.s.l. & $\alpha$ = 21.4\%  & T\textsubscript{air} [4] \newline H [4] \newline WV [3] \newline WD [1] &  L\textsubscript{up} [1] \newline L\textsubscript{down} [1] \newline S\textsubscript{up} [1] \newline S\textsubscript{down} [1]  \\ 
		\bottomrule
	\end{tabular*} 
		\raggedright
		\textsuperscript{2} Morphological parameters for the Sperrstrasse site were calculated for a 250 \si{\meter} circular area surrounding the study sites using the method described in \citet{Grimmond1999}. $z_H$: average building height, $\sigma_H $: standard deviation of building height, $\lambda_P $: plan aspect ratio, $\lambda_C $: complete aspect ratio, H/W: local canyon height to width ratio, $\alpha$: surface albedo. \\
		\textsuperscript{3} H: humidity, WV: wind velocity, WD: wind direction, P: pressure. \\
		\textsuperscript{4} L\textsubscript{up}: upwelling longwave radiation, L\textsubscript{down}: downwelling longwave radiation, S\textsubscript{up}: upwelling shortwave radiation, S\textsubscript{down}: downwelling shortwave radiation.
\end{table}

During an intensive observation period (IOP) in late June/early July 2002, the Sperrstrasse canyon was instrumented with an array of infrared thermometers (IRT) to view individual canyon facet T\textsubscript{surf} to sample representative road, roof, and wall surface temperatures (T\textsubscript{road}, T\textsubscript{roof}, and T\textsubscript{wall} respectively). Plan and complete aspect ratios for the Sperrstrasse canyon are used to compute weighting schemes to retrieve complete and plan surface temperatures (T\textsubscript{comp} and T\textsubscript{plan} respectively) at 30 minute intervals over the IOP. T\textsubscript{comp} represents a complete urban T\textsubscript{surf}, where facet temperatures are weighted and averaged based on their areal proportion of the complete urban surface area. T\textsubscript{plan} represents the Sperrstrasse site as viewed by a satellite or aerial remote sensor in the nadir. Weighting schemes for T\textsubscript{plan} and T\textsubscript{comp} are included in Table \ref{weightings}. Urban T\textsubscript{surf} derived from complete, plan, and hemispherical representations of the Sperrstrasse site are used to investigate the effect of sensor-surface geometry on remote sensed T\textsubscript{surf} and sUHI, and to quantify the magnitude of geometric biases over a range of time scales and synoptic conditions. For comparison of sUHI to air temperature UHI, canopy layer air temperature UHI (clUHI) magnitudes are calculated as the difference between urban and rural T\textsubscript{air} measured from 2 \si{\meter} above ground level.

@@

Figure \ref{heatsuhi} shows seasonal variations in diurnal patterns of mean monthly hemispherical sUHI magnitudes at 30 minute intervals for the eight month study period. The sUHI displays significant seasonal variation, largest in the daytime hours, and is strongly controlled by day length and solar angle. Nighttime sUHI does not vary significantly across seasons.

Figure \ref{heatcluhi} shows seasonal variations in diurnal patterns of mean monthly clUHI calculated at 30 minute intervals for the eight month study period. clUHI development is strongly controlled by the timing of sunset/sunrise cycles and displays the largest seasonal variance in the hours immediately after sunset. Daytime clUHI does not vary significantly across seasons. 
\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatsuhi}
	\caption{A heatmap of mean half hourly hemispherical sUHI for each month calculated at 30 \si{\min} intervals over the eight month study period. Results are interpolated between months.}
	\label{heatsuhi}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatatuhi}
	\caption{A heatmap of mean half hourly canopy layer UHI for each month calculated at 30 \si{\min} intervals from T\textsubscript{air} measured at approximately 2 \si{\meter} above ground level over the eight month study period. Results are interpolated between months.}
	\label{heatcluhi}
\end{figure}

@@

Figure \ref{bx_suhi_compare} shows sUHI magnitudes calculated from urban T\textsubscript{comp}, T\textsubscript{plan}, and T\textsubscript{hem}. Compared to complete sUHI; nadir and hemispherical views of the surface overestimate sUHI by day and underestimate sUHI by night. sUHI from a nadir view shows the greatest diurnal variance in sUHI, particularly under clear sky 'satellite friendly' conditions.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{bxsuhi1}
	\caption{A comparison of sUHI magnitudes from complete, hemispherical, and nadir remote sensed representations of the Sperrstrasse canyon over the IOP. Each plot includes mean sUHI, as well case days representing sUHI under clear sky and clouded sky conditions.}
	\label{bx_suhi_compare}
\end{figure}

@@

Figures \ref{meteo_kdown}, \ref{meteo_hum}, \ref{meteo_wv}, and \ref{meteo_atuhi} show sUHI magnitudes as a function of incoming solar radiation, water vapor content, wind velocity, and clUHI. Winter hours are omitted in Figures \ref{meteo_hum}, and \ref{meteo_wv}, and \ref{meteo_atuhi} as sUHI is small and displays minimal variation in winter. Both winter and nighttime hours are omitted in Figure \ref{meteo_kdown} to examine daytime sUHI under clear sky and clouded sky conditions.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{meteo_kdown}
	\caption{sUHI magnitude versus incoming solar radiation binned for clear sky (when the sum of daytime K\textsubscript{down} \textgreater 10000 \si{\watt \per \square \meter}) and cloudy sky days (when the sum of daytime K\textsubscript{down} \textless 10000 \si{\watt \per \square \meter})}
	\label{meteo_kdown}
\end{figure}

@@

\section{Discussion}

\subsection{Diurnal patterns of sUHI}

sUHI in Basel from complete, nadir, and hemispherical representations of T\textsubscript{surf} displays two diurnal peaks, the first in the late afternoon and a second just after sunset. Clear sky conditions amplify this phenomena. A late afternoon peak in sUHI is likely the result of the urban-rural contrasts in thermal admittance (and by relation, urban-rural soil moisture contrasts). The thermal admittance of many urban surfaces, particularly rooftops, tends to be lower than rural and vegetated environments \citep{Spronken-Smith1998} – particularly in temperate climates where rural soil moisture is largely maintained through summer. Lower urban thermal admittance manifests in a larger diurnal thermal amplitude and thus, greater daytime surface heating and nighttime surface cooling. Nadir and hemispherical views are biased towards low thermal admittance rooftop facets, and thus display large late afternoon peaks in sUHI.

A second peak in sUHI after sunset is the result of differences in relative cooling rates of urban and rural surfaces. In this case, nighttime sUHI is likely the result of canyon radiation trapping from obstructed canyon sky-view-factors. The second peak sUHI is largest following clear sky conditions when the potential for significant differentials in urban-rural nocturnal cooling rates is maximized. A second peak is observed across all representations of urban T\textsubscript{surf} but is most apparent in complete and nadir representations of sUHI, which, for the Sperrstrasse site, sample T\textsubscript{road} to a greater extent than the hemispherical view. A weak sUHI is maintained through the nighttime as urban and rural cooling rates reach parity in the hours after sunset \citep{Oke2017}. Minimum sUHI is observed just after sunrise, where sUHI magnitudes are occasionally negative. At low solar angles, shading by 3-dimensional urban geometry suppresses heating rates for a large portion of urban surface area, reducing overall urban heating rates in early morning. As solar angles increase through the morning and more facets experience direct isolation, sUHI develops, with nadir and hemispherical representations displaying more rapid intensification than complete sUHI from a bias towards low thermal admittance and directly sunlit rooftop surfaces.

>>>>

Inter-site comparison is the crux of UHI analysis, thus it is imperative that urban T\textsubscript{surf} measurements are representative of coherent urban patches and free from confounding influences (i.e. atmospheric and emissivity effects). Meta-analysis of the air temperature (T\textsubscript{air}) UHI literature shows that these goals are rarely satisfied \citep{Stewart2011}. Given the relative difficulty in retrieving accurate, representative urban T\textsubscript{surf}, similar conclusions are likely for sUHI analysis. In spite of this fact, and the short period over which large-scale, generalizable methods for measuring urban T\textsubscript{surf} have been available, study of sUHI via TIR remote sensing has expanded significantly in the last twenty years \citep{Peng2012,Voogt2003}. Using the method and parameterization described in Chapter \ref{paper1} twl long-term climatologies of hemispherical radiometric urban T\textsubscript{surf} (T\textsubscript{hem, r}) were derived from time continuous near-ground upwelling TIR as measured from an inverted pyrgeometer. The method, and an associated parameterization scheme, was developed to address and overcome biases inherent in traditional methods for urban T\textsubscript{surf} retrieval by providing temporally continuous, geometrically representative\footnote{A hemispherical view is not perfectly geometrically representative of urban surface geometry. This is best illustrated by visualizing an urban area from the perspective of a downward facing ‘fish-eye’ camera. Geometric sampling biases are a result of lens distortions and the sensor cosine response. However, by sampling the surface 3-dimensionally, T\textsubscript{hem, r} is more representative of urban geometry than conventional 2-dimensional views of the surface. The geometric representivity of urban T\textsubscript{hem, r} is discussed in section \ref{Methodological limitations and considerations}.} urban T\textsubscript{surf} under all-sky conditions for sUHI analysis. These measurements are often made as a part of the net radiation determination for urban energy balance studies.

@@

\subsection{A method to retrieve hemispherical radiometric urban T\textsubscript{surf}}
\label{method2}

@@

For each time step, these steps are repeated at an interval of 0.5 \si{\kelvin} for a predefined range of potential T\textsubscript{hem, r}, with results aggregated into a lookup table relating modeled irradiances to corrected T\textsubscript{hem, r} for the observed ambient T\textsubscript{air} and humidities. The measured irradiance is then matched with the closest modeled irradiance to return the associated corrected T\textsubscript{hem, r} for the target time step.

@@

Although MODTRAN has been show to accurately model radiative transfer of broadband longwave radiation at urban scale path lengths \citep{Hoch2005, Hoch2007}, the added complexity inherent in simulating fluxes of radiation hemispherically over complex urban terrain prompted an independent evaluation of the correction method using observations of upwelling longwave radiation (measured from 2 \si{\meter}, 10 \si{\meter}, and 30 \si{\meter} above ground level) over a planar surface for a continuous 16-day period. In the evaluation, a modified version of the method uses T\textsubscript{hem, b} inferred from the lowest L\textsubscript{up} measurement along with profiles of T\textsubscript{air} and humidity to model irradiances at 10 \si{\meter} and 30 \si{\meter} at each time step. Modeled and measured irradiances match well, over wide range of mid-latitude atmospheric conditions, with results summarized in Table \ref{evalstats}.

By virtue of requiring nearly 500 radiative transfer simulations per time step and significant post-processing, the method described in \ref{method2} is computationally expensive. This prompted the development of a parameterization scheme to facilitate more widespread usage of urban T\textsubscript{hem, r} for climatological and comparative sUHI analysis. In the parametrization, to reduce computational time, radiative transfer simulations are run for a single view factor weighted average path length representing the average distance from the surface to the sensor as "seen" by the sensor over its FOV. This view factor weighted "hemispherical" path length can be calculated using a sensor view model (such as SUM) or approximated by hand using a digital building model (although care should be taken to ensure the sensor cosine response is accurately represented). Using the view factor weighted path length, a suite of radiative transfer simulations is run prior to correction to retrieve "hemispherical" broadband atmospheric transmittances for a range of potential humidities. Humidity-transmittance pairings are aggregated into a lookup table (LUT), where the measured humidity at each time step can be matched with the associated hemispherical transmittance. Using the hemispherical transmittance as the fraction of surface emitted L\textsubscript{up} reaching the sensor, measured L\textsubscript{up} can then be decomposed into its surface and atmospheric emitted components, from which a parameterized T\textsubscript{hem, r} (T\textsubscript{hem, para}) is inferred. Comparison of T\textsubscript{hem, r} derived from the correction method and the parameterization show good agreement, the results of which are included in Figure \ref{para_eval} and Table \ref{parastats}.

@@

This study uses data from two long-term climatological campaigns: the Basel Urban Boundary Layer Experiment (BUBBLE) conducted over December 2001 through July 2002 in Basel, Switzerland \citep{Rotach2005}, and the Environmental Prediction in Canadian Cities (EPiCC) (CITE?) campaign in Vancouver, Canada. Using the method described in section \ref{method2}, an eight month climatology of T\textsubscript{hem, r} are retrieved from radiation and meteorological data collected as a part of the BUBBLE campaign. Urban data were observed from a tower located near city center at the "Basel Sperrstrasse" site. Rural reference data were observed at the "Lange Erlen" site approximately 6 \si{\kilo\meter} to the north east in the outskirts of the city of Basel.

During an intensive observation period (IOP) in late June/early July 2002, the Sperrstrasse canyon was instrumented with an array of infrared thermometers (IRT) to view individual canyon facet T\textsubscript{surf} to sample representative road, roof, and wall surface temperatures (T\textsubscript{road}, T\textsubscript{roof}, and T\textsubscript{wall} respectively). Plan and complete aspect ratios for the Sperrstrasse canyon are used to compute weighting schemes to retrieve complete and plan surface temperatures (T\textsubscript{comp} and T\textsubscript{plan} respectively) at 30 minute intervals over the IOP. T\textsubscript{comp} represents a complete urban T\textsubscript{surf}, where facet temperatures are weighted and averaged based on their areal proportion of the complete urban surface area. T\textsubscript{plan} represents the Sperrstrasse site as viewed by a satellite or aerial remote sensor in the nadir. Weighting schemes for T\textsubscript{plan} and T\textsubscript{comp} are included in Table \ref{weightings}. Urban T\textsubscript{surf} derived from complete, plan, and hemispherical representations of the Sperrstrasse site are used to investigate the effect of sensor-surface geometry on remote sensed T\textsubscript{surf} and sUHI, and to quantify the magnitude of geometric biases over a range of time scales and synoptic conditions. In addition, during the IOP, a second rural reference site ("Village Neuf"), located approximately 5 \si{\kilo\meter} SSE of the Sperrstrasse site, was used to investigate the influence of rural site characteristics on sUHI.

To supplement data from the BUBBLE campaign, radiation and meteorological variables observed as a part of the EPiCC project are used to derive a climatology of T\textsubscript{hem, r} for the year long period spanning October 2008 through September 2009 using the parameterization scheme. These data provide a second, long term, time continuous climatology of sUHI for comparison of seasonal and diurnal patterns, to understand the influence of urban and rural site selection and characteristics on sUHI, and to aid in developing a generalized model for sUHI development over multiple time scales.

Site morphologies and observed variables for BUBBLE and EPiCC sites are described in Tables \ref{morphbspr} and \ref{morphepicc}.

\begin{table}[H]
	\centering
	\caption{A description of morphological parameters and measured variables for BUBBLE urban and rural sites. Modified from \citet{Rotach2005} to include only relevant parameters.}
	\label{morphbspr}
	\begin{tabular*}{\textwidth}{p{3.75cm} p{2.25cm}p{3.5cm}p{2.75cm}p{2.75cm}}
		\toprule 
		Site & Location & Morphological & Meteorological & Radiation \\ 
		& Height & Characteristics\footnote{} & Variables\footnote{} & [No of levels]\footnote{} \\ 	\midrule

		Basel Sperrstrasse \newline \textit{Urban} \textit{street canyon} \newline LCZ: 2 & 47.57\si{\degree} N \newline 7.60\si{\degree} E \newline 255 \si{\meter} a.s.l. & $z_H$ = 14.6  \si{\meter} \newline $\sigma_H $ = 6.9 \si{\meter} \newline H/W = 0.54 \newline $\lambda_C $ = 0.37\newline $\lambda_S$ = 1.0 \newline $\alpha$ = 11.0\% & T\textsubscript{air} [7] \newline H [7] \newline WV [12] \newline WD [1] \newline P [1] & L\textsubscript{up} [3] \newline L\textsubscript{down} [5] \newline S\textsubscript{up} [2] \newline S\textsubscript{down} [3] \\ 
		& & & & \\
		Lange Erlen \newline \textit{Rural parkland} \newline LCZ: B/D & 47.59\si{\degree} N \newline 7.65\si{\degree} E \newline 275 \si{\meter} a.s.l. & $\alpha$ = 21.4\%  & T\textsubscript{air} [4] \newline H [4] \newline WV [3] \newline WD [1] &  L\textsubscript{up} [1] \newline L\textsubscript{down} [1] \newline S\textsubscript{up} [1] \newline S\textsubscript{down} [1]  \\ 
		&&&&\\
		Village Neuf \newline \textit{Rural farmland} \newline LCZ: D/F & 47.57\si{\degree} N \newline 7.56\si{\degree} E \newline 240 \si{\meter} a.s.l. & $\alpha$ = 19.2\%
		& T\textsubscript{air} [3] \newline H [3] \newline WV [2] \newline WD [1] &  L\textsubscript{up} [1] \newline L\textsubscript{down} [1] \newline
		S\textsubscript{up} [2] \newline S\textsubscript{down} [2]  \\ 
		\bottomrule
	\end{tabular*} 
		\raggedright
		\textsuperscript{2} Morphological parameters for the Sperrstrasse site were calculated for a 250 \si{\meter} circular area surrounding the study sites using the method described in \citet{Grimmond1999}. $z_H$: average building height, $\sigma_H $: standard deviation of building height, $\lambda_P $: plan aspect ratio, $\lambda_C $: complete aspect ratio, H/W: local canyon height to width ratio, $\alpha$: surface albedo. \\
		\textsuperscript{3} H: humidity, WV: wind velocity, WD: wind direction, P: pressure. \\
		\textsuperscript{4} L\textsubscript{up}: upwelling longwave radiation, L\textsubscript{down}: downwelling longwave radiation, S\textsubscript{up}: upwelling shortwave radiation, S\textsubscript{down}: downwelling shortwave radiation.
\end{table}

\begin{table}[H]
	\centering
	\caption{A description of morphological parameters and measured variables for EPiCC urban and rural sites.}
	\label{morphepicc}
	\begin{tabular*}{\textwidth}{p{3.75cm} p{2.25cm}p{3.5cm}p{2.75cm}p{2.75cm}}
		\toprule 
		Site & Location & Morphological & Meteorological & Radiation \\ 
		& Height & Characteristics\footnote{} & Variables & [No of levels] \\ 	\midrule

		Sunset Tower \newline \textit{Urban/Suburban neighborhood} \newline LCZ: 6 & 49.23\si{\degree} N \newline 123.07\si{\degree} W \newline 2.0 \si{\meter} a.s.l. & $z_H$ = 5.3 \si{\meter} \newline $\lambda_B $ = 0.29 \newline $\lambda_T $ = 0.15\newline $\lambda_V$ = 0.22 \newline $\lambda_I$ = 0.37 \newline $\alpha$ = 14.7\% & T\textsubscript{air} [1] \newline H [1] \newline WV [1] \newline WD [1] \newline P [1] & L\textsubscript{up} [1] \newline L\textsubscript{down} [1] \newline S\textsubscript{up} [1] \newline S\textsubscript{down} [1] \\ 
		& & & & \\
		Westham Island \newline \textit{Rural, unmanaged} \newline LCZ: D & 49.09\si{\degree} N \newline 123.18\si{\degree} W \newline 91.4 \si{\meter} a.s.l. & $\alpha$ = 20.6\%  & T\textsubscript{air} [2] \newline H [2] \newline WV [2] \newline WD [2] &  L\textsubscript{up} [1] \newline L\textsubscript{down} [1] \newline S\textsubscript{up} [1] \newline S\textsubscript{down} [1]  \\ 
		\bottomrule
	\end{tabular*} 
	\textsuperscript{5}$\lambda_B $: Plan area of buildings, $\lambda_T $: Plan area of trees, $\lambda_V $: Plan area of ground vegetation, $\lambda_I $: Plan area of impervious ground.
	\raggedright
\end{table}

\subsection{sUHI analysis}

sUHI and canopy later UHI (clUHI) magnitudes were calculated from T\textsubscript{hem, r} and T\textsubscript{air} (measured from 2 \si{\meter} above ground level) as $\Delta$T\textsubscript{(urban-rural)} at 30 \si{\min} intervals. Rural T\textsubscript{hem, b} was calculated via

\begin{equation}
\label{ruralt}
T_{hem,~ b} = \sqrt[4]{\frac{\epsilon L_z^\uparrow + (1 - \epsilon)L_{sky}^\downarrow}{\sigma}}
\end{equation}

\noindent where $L_z^\uparrow$ is at-sensor upwelling longwave radiation, $L_{sky}^\downarrow$ is at-sensor reflected downwelling longwave radiation, and emissivity ($\epsilon$) = 0.94. Sensitivity tests included in Section \ref{sensitivity} of the companion paper show that screen level irradiances ($ z $ = ~2 \si{\meter}) are not subject to significant effects from the intervening atmosphere and do not require atmospheric correction. Rural irradiances in this study were measured from approximately 2 \si{\meter} above ground, thus rural T\textsubscript{hem, b} is approximately equal to T\textsubscript{hem, r}.

To compare seasonal and diurnal patterns of sUHI and clUHI development over the BUBBLE campaign, mean monthly UHI magnitudes were normalized via,

\begin{equation}
\text{UHI}_{\text{norm}} = \frac{(\text{UHI} - \text{UHI}_{\text{min}})}{(\text{UHI}_{\text{max}} - \text{UHI}_{\text{min}})}
\label{uhinorm}
\end{equation}

\noindent with UHI\textsubscript{min} and UHI\textsubscript{max} referring to minimum and maximum mean monthly sUHI and clUHI values over the climatology. This normalization restricts mean monthly UHI magnitudes to a range of values between zero (mean monthly UHI\textsubscript{min} over the climatology) and one (mean monthly UHI\textsubscript{max} over the climatology).

To investigate the influence of rural site characteristics on Basel's sUHI, sUHI magnitudes are calculated using T\textsubscript{hem, b} inferred for a different rural site ("Village Neuf") over the summertime IOP. Observations at Village Neuf were intermittent and often discontinous. As such, a subset of nine partially-complete days was selected to represent T\textsubscript{hem, b} and sUHI over a range of cloud coverages, to investigate the influence of rural site characteristics and T\textsubscript{surf} regimes on sUHI. As sUHI develop, preference was given to days with continuois observations in early afternoon through night. For each of the nine days sUHI\textsubscript{max} was used to infer a normalized sUHI magnitude for both Lange Erlen and Village Neuf sites at 30- \si{\minute} intervals, to remove day-to and compare patterns of sUHI development for the two sites. Mean normalized sUHI was then calculated at each time step over the nine day period. A normalized T\textsubscript{hem, b} was also calculated (using maximum T\textsubscript{hem, b} for each day) to compare T\textsubscript{surf} regimes between the two sites.

@@

Figure \ref{heatsuhi} shows seasonal variations in diurnal patterns of mean monthly hemispherical sUHI magnitudes at 30 minute intervals for the BUBBLE campaign. The sUHI in Basel displays significant seasonal variation, largest in the daytime hours, and is strongly controlled by day length and solar angle. Nighttime sUHI does not vary significantly across seasons.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatsuhi}
	\caption{A heatmap of mean half hourly hemispherical sUHI for each month calculated at 30 \si{\min} intervals for the BUBBLE campaign. Results are interpolated between months.}
	\label{heatsuhi}
\end{figure}

Figure \ref{heatcluhi} shows seasonal variations in diurnal patterns of mean monthly clUHI calculated for the same study period as Figure \ref{heatsuhi}. clUHI development is strongly controlled by the timing of sunset/sunrise cycles and displays the largest seasonal variance in the hours immediately after sunset. Daytime clUHI does not vary significantly across seasons.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatatuhi}
	\caption{A heatmap of mean half hourly canopy layer UHI for each month calculated at 30 \si{\min} intervals for the BUBBLE campaign. Results are interpolated between months.}
	\label{heatcluhi}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heat_uhi_diff}
	\caption{A heatmap of the difference between mean half hourly hemispherical normalized sUHI and canopy layer UHI for each month calculated at 30 \si{\min} intervals over the BUBBLE campaign. Results are interpolated between months.}
	\label{heat_uhi_diff}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{vanc_suhi}
	\caption{A heatmap of mean half hourly hemispherical sUHI for each month calculated at 30 \si{\min} intervals for a year-long subset of the EPiCC campaign. Results are interpolated between months.}
	\label{vanc_suhi}
\end{figure}

@@

Figure \ref{bx_suhi_compare} shows sUHI magnitudes calculated from urban T\textsubscript{comp}, T\textsubscript{plan}, and T\textsubscript{hem}. Compared to sUHI viewed from a complete representation of the urban surface (sUHI\textsubscript{comp}); nadir (sUHI\textsubscript{nadir}) and hemispherical (sUHI\textsubscript{hem}) views of the surface overestimate sUHI\textsubscript{comp} by day and underestimate sUHI\textsubscript{comp} by night. sUHI\textsubscript{nadir} from a nadir view shows the greatest diurnal range of magnitudes, particularly under clear sky 'satellite friendly' conditions.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{bxsUHI_iop_bubble}
	\caption{A comparison of sUHI magnitudes from complete (sUHI\textsubscript{comp}), hemispherical (sUHI\textsubscript{hem}), and nadir (sUHI\textsubscript{nadir}) remote sensed representations of the Sperrstrasse canyon over the IOP. Each plot includes mean sUHI, as well case days representing sUHI under clear sky and clouded sky conditions.}
	\label{bx_suhi_compare}
\end{figure}

@@

Figures \ref{meteo_kdown}, \ref{meteo_hum}, \ref{meteo_wv}, and \ref{meteo_atuhi} show hemispherical sUHI magnitudes as a function of incoming solar radiation, water vapor content, wind velocity, and clUHI measured over the BUBBLE campaign. Winter hours are omitted in Figures \ref{meteo_hum}, and \ref{meteo_wv}, and \ref{meteo_atuhi} as sUHI is small and displays minimal variation in winter. Both winter and nighttime hours are omitted in Figure \ref{meteo_kdown} to examine daytime sUHI under clear sky and clouded sky conditions.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{meteo_kdown}
	\caption{sUHI magnitude versus incoming solar radiation binned for clear sky (when the sum of daytime K\textsubscript{down} \textgreater 18 \si{\mega\joule\per\meter\squared}) and cloudy sky days (when the sum of daytime K\textsubscript{down} \textless 18 \si{\mega\joule\per\meter\squared})}
	\label{meteo_kdown}
\end{figure}

@@

\pagebreak

\subsection{The effect of rural/non-urban characteristics on sUHI}

Figure \ref{rur_uhi_means} shows urban T\textsubscript{hem, r} from the Sperrstrasse site and rural T\textsubscript{hem, b} for the Lange Erlen and Village Neuf sites as well as their associated hemispherical sUHI magnitudes for a representative, summertime clear sky day. In addition, the figure shows mean normalized hemispherical sUHI and T\textsubscript{hem, b} (calculated from maximum sUHI and T\textsubscript{hem, b} values for each day) for the Lange Erlen and Village Neuf stations. Days were chosen to represent a wide range of summertime conditions and cloud coverages, however, observations at the Village Neuf site were intermittent and n = 9 only applies to hours after 12:00 LST when data could be continuously sampled.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{rur_uhi_means1}
	\caption{Top: T\textsubscript{hem} from the Sperrstrasse urban and Lange Erlen and Village Neuf sites and sUHI magnitudes calculated from the two rural stations for a representative summer clear sky day. Middle and bottom: Mean normalized hemispherical sUHI and T\textsubscript{hem, b} calculated for the Lange Erlen and Village Neuf sites. Data at Village Neuf before noon were intermittent, thus n = 9 only applies to values after 12:00 LST. Both sites are sampled over the same truncated period on days with incomplete data.}
	\label{rur_uhi_means}
\end{figure}

\section{Discussion}
\citet{Oke2017} presents a generalized conceptual model for sUHI development for multiple representations of the surface. However, the results in \citet{Oke2017} are based on simulations of an idealized urban area without trees, complex non-orthogonal surface geometry, or sloped facets and have not been supported observationally. The results in this paper provides an ideal platform to test conceptual understanding of sUHI development and to understand the diurnal and seasonal nature of sUHI.

\subsection{Diurnal patterns of sUHI}
\label{gen}

sUHI development is the result of differences in urban and rural heating and cooling rates. A variety of factors modify urban heating and cooling rates relative to non-urban spaces, most notably urban-rural contrasts in sky-view-factor, impervious surface fraction, and thermal admittance (and by relation, urban-rural soil moisture contrasts). These differences provide the genesis for diurnal sUHI development. Rural surfaces have more open (less obstructed) sky view factors, and respond quickly to insolation a low solar angles in the early morning hours. Shading by canyon features causes urban T\textsubscript{surf} to respond more slowly, resulting in a small sUHI\textsubscript{min} in the hours just after sunset. This is observed in Basel across all representations of urban T\textsubscript{surf} at similar magnitudes. Through the late morning hours, urban heating rates increase relative to rural rates as the solar angle increases and low thermal admittance facets (particularly rooftops) experience more direct insolation and quickly heat up. Increases in urban T\textsubscript{surf} are amplified by the abundance of impervious surfaces, which result in a smaller fraction of insolation partitioned to latent heat relative to vegetated non urban spaces. After the initial spike in rural heating in the morning hours, urban heating rates overtake rural and the sUHI slowly grows through midday. In the hours after midday, the solar angle decreases and both urban and rural heating rates decline and begin to converge, as shading by canyon geometry causes some facets to cool. sUHI reaches a peak at approximately two to three hours hours after solar noon.
